---
title       : Univariate regression analysis as a shiny app
subtitle    : Based on the mtcars dataset
author      : MLSports
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Problem

- Doing Univariate Linear Regression Analysis in R is "easy" (not really, but running the commands is quite easy!)
- Provide opportunity to play around for colleagues without experience in R
- Using a shiny app that is available to everyone
- Use mtcars data set
- Want to predict mpg (miles per gallon) by different continuous features

--- .class #id 

## Dataset
```{r loadining data set, echo=FALSE}
mpgData <- mtcars
```


- mtcars
- Data from the 1974 Motor Trend US magazine
- Comprises fuel consumption and 10 aspects of automobile design and performance 
- 32 automobiles (1973-74 models)
- `r colnames(mtcars)[1]` - Miles per gallon
- `r colnames(mtcars)[3]` - Displacement (cu. in.)
- `r colnames(mtcars)[4]` - Horse Power
- `r colnames(mtcars)[6]` - Weight
- `r colnames(mtcars)[7]` - 1/4 Mile Time



--- 
## Shiny app example
- https://mlsports.shinyapps.io/C_DevData/
- Compare Predictions for `r colnames(mtcars)[c(3,4,6,7)]` separately to predict `r colnames(mtcars)[1]`
- Investigate regression line fit to the data and a summary of the fit to compare models
```{r example, echo=FALSE, fig.height=5, fig.width=10}
fit<- lm(mpg~disp, data=mpgData)
plot(mpg~disp, 
            data = mpgData, pch=21, bg="lightblue")
abline(fit, col="red", lw=3)
```

---
## Outlook 
- Include non-continous features
- Include option for Multivariate Regression
- Extend application to arbitrary datasets

